### 2015-09-24 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Kat B edits

#Set some options
options(na.action='na.fail')
opts_knit$set(root.dir = '..')
opts_chunk$set(echo=FALSE,
               warning=FALSE,
               message=FALSE,
               fig.path='../Figures/',
               fig.width= 4,
               fig.height= 8,
               fig.show='asis',
               dev=c('png','pdf'))

@@

**Figure 3** Factors affecting early-life telomere length in Seychelles warblers at the individual level, within seasons. **A** Model averaged estimates and 95% confidence intervals for alxplanatory terms used in a linear model with telomere length as the response variable. Numbers in brackets are the relative importance of each term in the top model set (see main text for details; TQ = territory quality). **B** Presence/absence of helpers and **c** tarsus length in relation to raw telomere length in nestlings (black, solid lines) and fledglings (grey, dashed lines). Points and error bars in **B** are mean $\pm$ s.e., and the line and shaded areas from **C** represent fitted values and 95% confidence limits from a linear regression.

@@

**Figure 5** Kaplan-Meier curves showing the relationship between telomere length and survival for individual Seychelles warblers measured as chicks (**A**), and fledglings  (**B**). Telomere length is binned into groups here for visualisation purposes only (long and short = greater than or less than median telomere length, repectively).

@@

```{r Figure 1,fig.width=5,fig.height=9}
######################
#1A
######################

@@

```{r Figure 2,fig.width=5,fig.height=9}

@@

Fig2A <- ggplot(juvseason,
       aes(x = Insect,
           y = TLKBmean,
           col = Season)) +
  ylab('Telomere length') + 
  xlab('Food availability') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_pointrange(aes(ymin=TLKBmean-TLKBse,ymax=TLKBmean+TLKBse)) +
  stat_smooth(method = 'lm',se = T,col = 'black') +
  scale_color_manual(values = c('black',grey(0.4))) +
  annotate('text',label = 'A',x=-1.5,y=8)

@@

Fig3C <- ggplot(juv,
                aes(x = Tarsus,
                    y = TLKB,
                    col=Fledged,
                    lty = Fledged)) +
  ylab('Telomere length (kb)') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_point(size=3) +
  stat_smooth(method = 'lm',se = T) +
  scale_color_manual(values = c('black',grey(0.4))) +
  annotate('text',label = 'C',x=19,y=15)

>>>>

#Set some options
options(na.action='na.fail')
opts_knit$set(root.dir = '..')
opts_chunk$set(echo=FALSE,
               warning=FALSE,
               message=FALSE,
               fig.path='../Figures/',
               fig.show='asis',
               dev=c('png','pdf'))

@@

**Figure 3** Factors affecting early-life telomere length in Seychelles warblers at the individual level, within seasons. **A** Model averaged estimates and 95% confidence intervals for explanatory terms used in a linear model with telomere length as the response variable. Numbers in brackets are the relative importance of each term in the top model set (see main text for details; TQ = territory quality). **B** Presence/absence of helpers and **c** tarsus length in relation to raw telomere length in nestlings (black, solid lines) and fledglings (grey, dashed lines). Points and error bars in **B** are mean $\pm$ s.e., and the line and shaded areas from **C** represent fitted values and 95% confidence limits from a linear regression.

@@

**Figure 5** Kaplan-Meier curves showing the relationship between telomere length and survival for individual Seychelles warblers measured as chicks (**A**), and fledglings  (**B**). Telomere length is binned into groups here for visualisation purposes only (long and short = greater than or less than median telomere length, respectively).

@@

```{r Figure 1,fig.width=4,fig.height=8}
######################
#1A
######################

@@

```{r Figure 2,fig.width=4,fig.height=8}

@@

Fig2A <- ggplot(juvseason,
       aes(x = Insect,
           y = TLKBmean,
           col = Season)) +
  ylab('Telomere length (kb)') + 
  xlab('Food availability') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_pointrange(aes(ymin=TLKBmean-TLKBse,ymax=TLKBmean+TLKBse)) +
  stat_smooth(method = 'lm',se = T,col = 'black') +
  scale_color_manual(values = c('black',grey(0.4))) +
  annotate('text',label = 'A',x=-1.5,y=8)

@@

Fig3C <- ggplot(juv,
                aes(x = Tarsus,
                    y = TLKB,
                    col = Fledged,
                    lty = Fledged)) +
  ylab('Telomere length (kb)') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_point(size=3) +
  stat_smooth(method = 'lm',se = T) +
  scale_color_manual(values = c('black',grey(0.4))) +
  annotate('text',label = 'C',x=19,y=15)
